\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories

### 2023-09-25 paper.tex
update

For forbidden region in the shape of a hyperplane $\mathcal{L}(\tilde{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}). The reachability constraint now can then be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$. When transformed into canonical frame, the hyperplane can be written as $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$, where,
  \begin{equation}
    n_\cE = H(q_1,q_2)n, \quad d_\cE =-\vn\transpose o + d.
\end{equation}
Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$).

@@

  \begin{proposition}\label{prop:dpi_ne_dt}
    The differential of the projection function $\pi^\cE_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
    \begin{equation}
      \partial_q \pi^\cE_{\vn \cE}(q) = \begin{cases}
        \partial_q p^\cE_{t1}-\partial_q p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
        \partial_q p^\cE_{t2}-\partial_q p^\cE_{\cL} &  d \in [- d_{\cE t},0), \\
        {0} & otherwise.
      \end{cases}
    \end{equation}
    where
    \begin{multline}
      \partial_q p_\cL =   (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \\
      + \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2},
    \end{multline}
    \begin{equation}
      \partial_q p_{1} =  -\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} 
      + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}}.
    \end{equation}
  \end{proposition}
  \begin{proof}
  See \Cref{proof:dpi_ne_dt}.
  \end{proof}
  Based on the previous proposition, the differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
  \begin{equation}
    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}
  \end{equation}

@@

For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied. 
Assume the segment has endpoints $p_1$ and $p_2$; then the segment can be defined as:
\begin{equation}
\bmat{(p_1-p_2)\transpose\\(p_2-p_1)\transpose} p \leq \bmat{p_2\transpose\\-p_1\transpose}(p_1-p_2)
\end{equation}
\rtron{Needs an additiona constraint that $p$ needs to be on the line $p_1p_2$.}
\begin{constraint}[Line-segment-ellipsoid reachability constraint]
\begin{align}
D(\vq) &=  \begin{cases}
D_1(p_1) & (p_1-p_2)\transpose (p_{\cL}-p_2)<0\\
D_1(p_2) & (p_2-p_1)\transpose (p_{\cL}-p_1)<0\\
D_2(p_{\cL}) & \textrm{otherwise}
\end{cases} \label{eq:segment_ellipsoid_constraint}\\
  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\\
   \Pi_\sZ(z) & = 0, 
\end{align}
\end{constraint}

>>>>

For forbidden region in the shape of a hyperplane $\mathcal{L}(\Eframe{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}). The reachability constraint now can then be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$. When transformed into canonical frame, the hyperplane can be written as $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$, where,
  \begin{equation}
    n_\cE = H(q_1,q_2)n, \quad d_\cE =-\vn\transpose o + d.
\end{equation}
Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$).

@@

  \begin{proposition}\label{prop:dpi_ne_dt}
    The differential of the projection function $\pi^\cE_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
    \begin{equation}
      \partial_q \pi^\cE_{\vn \cE}(q) = \begin{cases}
        \partial_q p^\cE_{t1}-\partial_q p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
        \partial_q p^\cE_{t2}-\partial_q p^\cE_{\cL} &  d \in [- d_{\cE t},0), \\
        {0} & otherwise.
      \end{cases}
    \end{equation}
    where
    \begin{multline}
      \partial_q p_\cL =   (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \\
      + \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2},
    \end{multline}
    \begin{equation}
      \partial_q p_{1} =  -\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} 
      + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}}.
    \end{equation}
  \end{proposition}
  \begin{proof}
  See \Cref{proof:dpi_ne_dt}.
  \end{proof}
  Based on the \Cref{prop:dpi_ne_dt}, the differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
  \begin{equation}
    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}
  \end{equation}

@@

For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied. 
Assume the segment on hyperplane $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$ has endpoints $p_1$ and $p_2$; then the segment can be defined as:
\begin{equation}
\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), 
\end{equation}
\rtron{Needs an additiona constraint that $p$ needs to be on the line $p_1p_2$.}
\begin{constraint}[Line-segment-ellipsoid reachability constraint]
\begin{align}
D(\vq) &=  \begin{cases}
D_1(p_1) & (p_1-p_2)\transpose (p_{\cL}-p_2)<0\\
D_1(p_2) & (p_2-p_1)\transpose (p_{\cL}-p_1)<0\\
D_2(p_{\cL}) & \textrm{otherwise}
\end{cases} \label{eq:segment_ellipsoid_constraint}\\
  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\\
   \Pi_\sZ(z) & = 0, 
\end{align}
\end{constraint}
